\bf Service Chain Placement in SDNs \thanks{Research supported in part by Network Programming (Neptune) Consortium, Israel.}

### 2018-01-07 src/chain.tex
fix dp for fault

\subsection{Fault Tolerance on Layered Graph}
We first assume that the input graph is a directed layered graph, i.e.
$G = (\bigcup_{i = 1}^l L_i, A)$ where 
$A \subseteq \bigcup_{i = 1}^{l - 1} L_i \times L_{i+1}$.
We assume that the number of vertices in each layer is at least two, or otherwise a 2-robust 
placement does not exist.
The algorithm uses dynamic programming.
We find the optimal 2-robust placement for every  
combination of two physical vertices from the same layer, 
and every combination of two virtual functions.
Formally, given the input $(G = (V, E), \calG = (\calV, \calE), p, b, s, t, c)$
We define $ft(v_1, v_2, \alpha_1, \alpha_2)$ to be the optimal 2-robust placement of 2 chains
that start at $\sigma$ and end at $\alpha_1, \alpha_2$ respectively into 
(internal vertex disjoint) physical paths that start at $s$ and end at $v_1,v_2$ respectively.
One can verified that the following recursive formula holds:
$$
ft(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = \min
\begin{cases}
nn(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2)
\\
ny(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2)
\\
yn(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2)
\\
yy(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) 
\end{cases}
$$

where
$$
\begin{array}{l}
nn(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = 
\displaystyle\smashoperator{\min_{\substack{\\ u_1, u_2: \\ b(u_1, v_1) \geq b(\gamma_1, \beta_1) \\ b(u_2, v_2) \geq b(\gamma_2, \beta_2)}}}
ft(u_1, u_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2)
\\
ny(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = 
\displaystyle\smashoperator{\min_{
	\substack{
	u_1, u_2: 
	\\ 
	b(u_1, v_1) \geq b(\gamma_1, \beta_1) 
	\\ 
	b(u_2, v_2) \geq b(\gamma_2, \beta_2)
	\\
	\gamma'_2\beta'_2 \in \calE:
	\\
	\beta'_2 \prec \gamma_2 
	}}}
ft(u_1, u_2, \alpha_1, \gamma_2, \gamma_1\beta_1, \gamma'_2\beta'_2)
\\
yn(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = 
\displaystyle\smashoperator{\min_{
	\substack{
	u_1, u_2: 
	\\ 
	b(u_1, v_1) \geq b(\gamma_1, \beta_1) 
	\\ 
	b(u_2, v_2) \geq b(\gamma_2, \beta_2)
	\\
	\gamma'_1\beta'_1 \in \calE:
	\\
	\beta'_1 \prec \gamma_1 
	}}}
ft(u_1, u_2, \gamma_1, \alpha_2, \gamma'_1\beta'_1, \gamma_2\beta_2)
\\
yy(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = 
\displaystyle\smashoperator{\min_{
	\substack{
	u_1, u_2: 
	\\ 
	b(u_1, v_1) \geq b(\gamma_1, \beta_1) 
	\\ 
	b(u_2, v_2) \geq b(\gamma_2, \beta_2)
	\\
	\gamma'_1\beta'_1, \gamma'_2\beta'_2 \in \calE:
	\\
	\beta'_1 \prec \gamma_1, \beta'_2 \prec \gamma_2 
	}}}
ft(u_1, u_2, \gamma_1, \gamma_2, \gamma'_1\beta'_1, \gamma'_2\beta'_2)
\end{array}
$$

>>>>

\subsection{Fault Tolerance on Layered Graph}
We first assume that the input graph is a directed layered graph, i.e.
$G = (\bigcup_{i = 1}^l L_i, A)$ where 
$A \subseteq \bigcup_{i = 1}^{l - 1} L_i \times L_{i+1}$.
We assume that the number of vertices in each layer is at least two, or otherwise a 2-robust 
placement does not exist.
The algorithm uses dynamic programming.
We find the optimal 2-robust placement for every  
combination of two physical vertices from the same layer, 
and every combination of two virtual functions.
Formally, given the input $(G = (V, E), \calG = (\calV, \calE), p, b, s, t, c)$
We define $ft(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2)$ 
to be the minimum cost of a 2-robust placement of 2 chains
that start at $\sigma$ and end at $\alpha_1, \alpha_2$ respectively into 
(internal vertex disjoint) physical paths that start at $s$ and end at $v_1,v_2$ respectively.
the placement is restricted to place a path of virtual functions from $\beta_1$ to
$\alpha_1$ and from $\beta_2$ to $\alpha_2$ into a single physical node respectively.
One can verified that the following recursive formula holds:
$$
ft(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = \min
\begin{cases}
nn(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2)
\\
ny(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2)
\\
yn(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2)
\\
yy(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) 
\end{cases}
$$

where
$$
\begin{array}{ll}
nn(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = 
\\ &
\displaystyle\smashoperator{\min_{\substack{\\ u_1, u_2: \\ b(u_1, v_1) \geq 
b(\gamma_1, \beta_1) \\ b(u_2, v_2) \geq b(\gamma_2, \beta_2)}}}
ft(u_1, u_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2)
%
\\
ny(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) = 
\\ &
\displaystyle\smashoperator{\min_{
	\substack{
	u_1, u_2: 
	\\ 
	b(u_1, v_1) \geq b(\gamma_1, \beta_1) 
	\\ 
	b(u_2, v_2) \geq b(\gamma_2, \beta_2)
	\\
	\gamma'_2\beta'_2 \in \calE:
	\\
	\beta'_2 \prec \gamma_2 
	}}}
ft(u_1, u_2, \alpha_1, \gamma_2, \gamma_1\beta_1, \gamma'_2\beta'_2) +
\\ & 
\cost_{v_2}(\beta_2 \leadsto \alpha_2) 
%
\\
yn(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) =
\\ & 
\displaystyle\smashoperator{\min_{
	\substack{
	u_1, u_2: 
	\\ 
	b(u_1, v_1) \geq b(\gamma_1, \beta_1) 
	\\ 
	b(u_2, v_2) \geq b(\gamma_2, \beta_2)
	\\
	\gamma'_1\beta'_1 \in \calE:
	\\
	\beta'_1 \prec \gamma_1 
	}}}
ft(u_1, u_2, \gamma_1, \alpha_2, \gamma'_1\beta'_1, \gamma_2\beta_2) + 
\\ & 
\cost_{v_1}(\beta_1 \leadsto \alpha_1) 
%
\\
yy(v_1, v_2, \alpha_1, \alpha_2, \gamma_1\beta_1, \gamma_2\beta_2) =
\\ & 
\displaystyle\smashoperator{\min_{
	\substack{
	u_1, u_2: 
	\\ 
	b(u_1, v_1) \geq b(\gamma_1, \beta_1) 
	\\ 
	b(u_2, v_2) \geq b(\gamma_2, \beta_2)
	\\
	\gamma'_1\beta'_1, \gamma'_2\beta'_2 \in \calE:
	\\
	\beta'_1 \prec \gamma_1, \beta'_2 \prec \gamma_2 
	}}}
ft(u_1, u_2, \gamma_1, \gamma_2, \gamma'_1\beta'_1, \gamma'_2\beta'_2) + 
\\
& \cost_{v_1}(\beta_1 \leadsto \alpha_1) + \cost_{v_2}(\beta_2 \leadsto \alpha_2) 
\end{array}
$$
